Reanalysis Step 6: Sensitivity Analysis and E-values

### 2025-09-01 reanalysis-6-sensitivity.qmd
sensitivity analysis bugs

@@

# Create E-value plot
bias_plot <- bias_plot(evalue_point, evalue_ci)

# Display the plot
print(bias_plot)
```

@@

    sub_coef <- coef(summary(sub_model))["ever_lapse_binary", ]

@@

>>>>

# Also extract RR values for bias_plot
rr_point <- evalue_result["RR", "point"]
rr_lower <- evalue_result["RR", "lower"]
rr_upper <- evalue_result["RR", "upper"]

@@

# Create E-value plot using RR values
# bias_plot expects RR values, not E-values
tryCatch({
  # The bias_plot function expects the RR estimate and its bounds
  bias_plot_obj <- bias_plot(rr_point, rr_lower)
  print(bias_plot_obj)
}, error = function(e) {
  cat("Note: Bias plot could not be generated.\n")
  cat("Error: ", e$message, "\n")
  cat("RR point: ", rr_point, ", RR lower: ", rr_lower, "\n")
})
```

@@

    sub_coef <- coef(summary(sub_model))["ever_lapse_binary1", ]

@@

  coef_lapse <- coef(summary(model))["ever_lapse_binary1", ]
